### 2020-12-18 written/eLifeRevision/Bittner_eLife2020.tex
STG section update

Distribution contours of emergent property value error are shown at levels of $2.5 \times 10^{-5}$, $5 \times 10^{-5}$, $1 \times 10^{-4}$, $2 \times 10^{-4}$, and $4 \times 10^{-4}$ (dark to light gray). 

>>>>

Distribution contours of hub neuron frequency from mean of .55 Hz are shown at levels of $.525$, $.53$, ... $.575$ Hz (dark to light gray away from mean).
Frequencies are averages over the stochasticity of the model.
